---
title: "Trial-level analyses"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)
```

This code reproduces the trial-level analyses reported in the following manuscript:

[Cosme, D., Mobasser, A., & J. H. Pfeifer. If you’re happy and you know it: Neural correlates of self-evaluated psychological health and well-being](https://psyarxiv.com/86n3b/)

# load packages
```{r, message=FALSE, warning=FALSE}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse, gtools, GGally, sjstats, lme4, lmerTest, knitr, ggeffects, kableExtra, install = TRUE)
```

# define aesthetics
```{r}
rois = c("#006989", "#56445D", "#8EC922")
constructs = c("#FEC601", "#F43C13", "#254E70")
instructions = wesanderson::wes_palette("Darjeeling1", 2, "continuous")
valence = c("#119DA4", "#19647E")
plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

# load data
```{r}
task = read.csv("task_data.csv", stringsAsFactors = FALSE)
betas = read.csv("neuro_data.csv", stringsAsFactors = FALSE)
```

# tidy
* Recode incorrectly named constructs
* Recode negative responses (e.g. no on reversed item = yes) in the social facet

```{r}
data = task %>%
  extract(subjectID, "subNum", "FP([0-9]{3})", remove = FALSE) %>%
  mutate(construct = ifelse(item == "lonely", "social", 
                     ifelse(item == "angry", "ill-being", construct)),
         reversed = ifelse(item == "lonely", 1, 
                    ifelse(item == "angry", 0, reversed)),
         instruction = as.factor(instruction),
         construct = as.factor(construct),
         item = as.character(item),
         RT = ifelse(RT == "NaN", NA, RT),
         RT = log(RT) - mean(log(RT), na.rm = TRUE),
         response = ifelse(response == 1, "yes",
                    ifelse(response == 2, "no", NA)),
         responseNum = ifelse(response == "yes" & reversed == 0, 1,
                       ifelse(response == "yes" & reversed == 1, 0,
                       ifelse(response == "no" & reversed == 0, 0,
                       ifelse(response == "no" & reversed == 1, 1, response)))),
         responseNum = as.integer(responseNum),
         responseYN = ifelse(responseNum == 1, "yes",
                      ifelse(responseNum == 0, "no", responseNum)),
         valence = ifelse(construct %in% c("well-being", "social") & reversed == 0, "positive",
                   ifelse(construct %in% c("well-being", "social") & reversed == 1, "negative",
                   ifelse(construct %in% "ill-being" & reversed == 0, "negative",
                   ifelse(construct %in% "ill-being" & reversed == 1, "positive", NA)))),
         valence = as.factor(valence)) %>%
  ungroup() %>%
  mutate(responseYN = as.factor(responseYN))

# relevel factors
data$valence = relevel(data$valence, "positive")
data$construct = relevel(data$construct, "well-being")
```

# exclude outliers and standardize
* Subset self trials
* Exclude outlier trials that are > 3 SDs from roi median across participants

```{r}
trial_conditions = data %>%
  select(subjectID, trial, run, instruction)

betas_outlier = betas %>%
  left_join(., trial_conditions) %>%
  filter(instruction == "self") %>%
  group_by(roi) %>%
  mutate(median = median(meanPE, na.rm = TRUE),
         sd3 = 3*sd(meanPE, na.rm = TRUE),
         outlier = ifelse(meanPE > median + sd3 | meanPE < median - sd3, "yes", "no")) 

betas_outlier %>%
  group_by(outlier) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(total = sum(n),
         percent = round((n / total) * 100, 2)) %>%
  kable(format = "pandoc")

betas_ex = betas_outlier %>%
  filter(outlier == "no") %>%
  select(-c(median, sd3, outlier))
```

# merge data and exclude participants
* Motion exclusions: FP091
* Technical failure: FP080, FP082
* Non-compliance: FP021, FP049, FP085, FP121
* Standardize within participant and ROI

```{r}
data_ex = data %>%
  left_join(., betas_ex) %>%
  filter(!subjectID %in% c("FP091", "FP080", "FP082", "FP021", "FP049", "FP085", "FP121")) %>%
  filter(!is.na(meanPE)) %>%
  filter(instruction == "self") %>%
  group_by(roi, subjectID) %>%
  mutate(std = meanPE / sd(meanPE, na.rm = TRUE)) %>%
  select(-sdPE)
```

# remove missing data for MLM analysis
```{r}
data_complete_mod = data_ex %>%
  select(-meanPE) %>%
  spread(roi, std) %>%
  select(subjectID, trial, run, construct, item, responseYN, RT, pgACC, vmPFC, VS) %>%
  na.omit()
```

# ROI descriptives 
```{r}
# correlations
pgACC_vmPFC = data_complete_mod %>%
   mutate(subjectID = as.factor(subjectID)) %>%
   select(subjectID, pgACC, vmPFC) %>%
   rmcorr::rmcorr(subjectID, pgACC, vmPFC, .)

pgACC_VS = data_complete_mod %>%
   mutate(subjectID = as.factor(subjectID)) %>%
   select(subjectID, pgACC, VS) %>%
   rmcorr::rmcorr(subjectID, pgACC, VS, .)

vmPFC_VS = data_complete_mod %>%
   mutate(subjectID = as.factor(subjectID)) %>%
   select(subjectID, vmPFC, VS) %>%
   rmcorr::rmcorr(subjectID, vmPFC, VS, .)

# means and SDs
mean_table = data_complete_mod %>%
  gather(roi, value, pgACC, vmPFC, VS) %>%
  group_by(roi) %>%
  summarize(M = round(mean(value, na.rm = TRUE), 2),
            SD = round(sd(value, na.rm = TRUE), 2)) %>%
  mutate(order = ifelse(roi == "pgACC", 1,
                 ifelse(roi == "vmPFC", 2, 3)),
         roi = ifelse(roi == "pgACC", "1. pgACC",
               ifelse(roi == "vmPFC", "2. vmPFC", "3. VS"))) %>%
  rename("ROI" = roi) %>%
  arrange(order) %>%
  select(-order)

# table
corr_table = data.frame(ROI = c("1. pgACC", "2. vmPFC", "3. VS"),
           `1` = c("--", paste0(round(pgACC_vmPFC[[1]],2), " [",round(pgACC_vmPFC[[4]][1],2),", ",round(pgACC_vmPFC[[4]][2],2),"]"),
                   paste0(round(pgACC_VS[[1]],2), " [",round(pgACC_VS[[4]][1],2),", ",round(pgACC_VS[[4]][2],2),"]")),
           `2` = c("", "--", paste0(round(vmPFC_VS[[1]],2), " [",round(vmPFC_VS[[4]][1],2),", ",round(vmPFC_VS[[4]][2],2),"]")),
           `3` = c("", "", "--"),
           check.names = FALSE)

mean_table %>%
  full_join(., corr_table) %>%
  knitr::kable(format = "pandoc", caption = "Repeated Measures Correlations Between ROIs (n = 3694). All correlations are statistically significant, p < .001. 95% confidence intervals are bracketed")
```

# RT models {.tabset}
These are the primary analyses reported in the main text of the manuscript, controlling for reaction time.

## run models {.tabset}
### compare models
Determine the best fitting model.

`model_0_rt` = Base model including including no ROIs

`model_1_rt` = Main effects model including ROIs

`model_2_rt` = Interaction model including ROIs and their interactions with well-being construct

```{r}
model_0_rt = glmer(responseYN ~ construct * RT + 
                     (1 | subjectID), 
                family = binomial, 
                data = data_complete_mod, control = glmerControl(optimizer = "bobyqa"))

model_1_rt = glmer(responseYN ~ construct * RT + pgACC + vmPFC + VS + 
                     (1 | subjectID), 
                family = binomial, 
                data = data_complete_mod, control = glmerControl(optimizer = "bobyqa"))

model_2_rt = glmer(responseYN ~ RT*construct + pgACC*construct + vmPFC*construct + VS*construct +
                     (1 | subjectID), 
                family = binomial, 
                data = data_complete_mod, control = glmerControl(optimizer = "bobyqa"))

# compare models
anova(model_0_rt, model_1_rt, model_2_rt)
```

### calculate R2
Compare the model R2 for the best fitting compared to the base model.

```{r}
performance::r2(model_0_rt)
performance::r2(model_2_rt)
```

### check variance inflation in the best fitting model
```{r}
# vif
car::vif(model_2_rt)
```

## model summary
```{r}
summary(model_2_rt)
```

## model table
```{r}
model_2_rt %>%
  broom.mixed::tidy(., conf.int = TRUE) %>%
  filter(effect == "fixed") %>%
  rename("SE" = std.error,
         "z" = statistic,
         "p" = p.value) %>%
  mutate(term = gsub("\\(Intercept\\)", "Intercept (well-being)", term),
         term = gsub("log\\(RT\\)", "RT", term),
         term = gsub("constructill-being", "Construct (ill-being)", term),
         term = gsub("constructsocial", "Construct (social)", term),
         term = gsub(":", " x ", term),
         p = ifelse(p < .001, "< .001",
                    ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
         `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high),
         z = abs(round(z, 2))) %>%
  select(term, `b [95% CI]`, z, p) %>%
  kable() %>%
  kableExtra::kable_styling()
```


## marginal probabilities {.tabset}
### all
```{r}
ggeffect(model_2_rt)
```

### PCC
```{r}
ggeffect(model_2_rt, terms = c("construct", "pgACC [0, 1]")) %>%
  data.frame() %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", predicted, conf.low, conf.high)) %>%
  kable() %>%
  kableExtra::kable_styling()
  
```

### vmPFC
```{r}
ggeffect(model_2_rt, terms = c("construct", "vmPFC [0, 1]")) %>%
  data.frame() %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", predicted, conf.low, conf.high)) %>%
  kable() %>%
  kableExtra::kable_styling()
  
```

### VS
```{r}
ggeffect(model_2_rt, terms = c("construct", "VS [0, 1]")) %>%
  data.frame() %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", predicted, conf.low, conf.high)) %>%
  kable() %>%
  kableExtra::kable_styling()
  
```

## plot predicted effects {.tabset}
### by construct
```{r}
logit2prob = function(logit){
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}

raw_values = data_complete_mod %>%
  select(subjectID, construct, RT, pgACC, vmPFC, VS)

raw_values$predicted_logit = predict(model_2_rt, newdata = raw_values, re.form = as.formula("~(1 | subjectID)"))

raw_values = raw_values %>%
  gather(roi, x, pgACC, VS, vmPFC) %>%
  rename("group" = construct) %>%
  mutate(predicted = logit2prob(predicted_logit))

vals = seq(round(min(raw_values$x),1), round(max(raw_values$x), 1), .2)

predicted = ggeffect(model_2_rt, terms = c("pgACC [vals]", "construct")) %>%
  data.frame() %>%
  mutate(roi = "pgACC") %>%
  bind_rows(ggeffect(model_2_rt, terms = c("VS [vals]", "construct")) %>%
    data.frame() %>%
    mutate(roi = "VS")) %>%
  bind_rows(ggeffect(model_2_rt, terms = c("vmPFC [vals]", "construct")) %>%
    data.frame() %>%
    mutate(roi = "vmPFC"))

predicted %>%
  ggplot(aes(x, predicted, fill = group)) +
  geom_point(data = raw_values, aes(color = group), alpha = .1, size = .5) + 
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2) +
  geom_line(aes(color = group), size = 1.5) +
  facet_grid(~roi) +
  scale_color_manual(values = constructs, name = "") + 
  scale_fill_manual(values = constructs, name = "") + 
  scale_x_continuous(breaks = seq(-6, 6, 2)) +
  labs(x = "\nparameter estimate (SD)", y = "probability of responding yes\n") + 
  plot_aes
```

### by ROI
```{r}
predicted %>%
  ggplot(aes(x, predicted, fill = roi)) +
  geom_point(data = raw_values, aes(color = roi), alpha = .1, size = .5) + 
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2) +
  geom_line(aes(color = roi), size = 1.5) +
  facet_grid(~group) +
  scale_color_manual(values = rois, name = "") + 
  scale_fill_manual(values = rois, name = "") + 
  scale_x_continuous(breaks = seq(-6, 6, 2)) +
  labs(x = "\nparameter estimate (SD)", y = "probability of responding yes\n") + 
  plot_aes
```

### RT
```{r}
raw_values = data_complete_mod %>%
  select(subjectID, construct, RT, pgACC, vmPFC, VS)

raw_values$predicted_logit = predict(model_2_rt, newdata = raw_values, re.form = as.formula("~(1 | subjectID)"))

raw_values = raw_values %>%
  rename("group" = construct,
         "x" = RT) %>%
  mutate(predicted = logit2prob(predicted_logit))

vals = seq(round(min(raw_values$x),1), round(max(raw_values$x), 1), .1)

ggeffect(model_2_rt, terms = c("RT [vals]", "construct")) %>%
  data.frame() %>%
  ggplot(aes(x, predicted, fill = group, group = group)) +
  geom_point(data = raw_values, aes(color = group), alpha = .2, size = .5) + 
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2) +
  geom_line(aes(color = group), size = 1.5) +
  scale_color_manual(values = constructs, name = "") + 
  scale_fill_manual(values = constructs, name = "") + 
  labs(x = "\nRT (s)", y = "probability of responding yes\n") + 
  plot_aes
```

# no RT model {.tabset}
These are the original preregistered analyses not controlling for reaction time, reported in supplementary material.

## run model
```{r}
model_2 = glmer(responseYN ~ construct + pgACC*construct + vmPFC*construct + VS*construct +
                     (1 | subjectID), 
                family = binomial, 
                data = data_complete_mod, control = glmerControl(optimizer = "bobyqa"))
```

## model summary
```{r}
summary(model_2)
```

## model table
```{r}
model_2 %>%
  broom.mixed::tidy(., conf.int = TRUE) %>%
  filter(effect == "fixed") %>%
  rename("SE" = std.error,
         "z" = statistic,
         "p" = p.value) %>%
  mutate(term = gsub("\\(Intercept\\)", "Intercept (well-being)", term),
         term = gsub("log\\(RT\\)", "RT", term),
         term = gsub("constructill-being", "Construct (ill-being)", term),
         term = gsub("constructsocial", "Construct (social)", term),
         term = gsub(":", " x ", term),
         p = ifelse(p < .001, "< .001",
                    ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
         `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high),
         z = abs(round(z, 2))) %>%
  select(term, `b [95% CI]`, z, p) %>%
  kable() %>%
  kableExtra::kable_styling()
```

## marginal probabilities {.tabset}
### all
```{r}
ggeffect(model_2)
```

### PCC
```{r}
ggeffect(model_2, terms = c("construct", "pgACC [0, 1]")) %>%
  data.frame() %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", predicted, conf.low, conf.high)) %>%
  kable() %>%
  kableExtra::kable_styling()
  
```

### vmPFC
```{r}
ggeffect(model_2, terms = c("construct", "vmPFC [0, 1]")) %>%
  data.frame() %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", predicted, conf.low, conf.high)) %>%
  kable() %>%
  kableExtra::kable_styling()
  
```

### VS
```{r}
ggeffect(model_2, terms = c("construct", "VS [0, 1]")) %>%
  data.frame() %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", predicted, conf.low, conf.high)) %>%
  kable() %>%
  kableExtra::kable_styling()
  
```

## plot {.tabset}
### by construct
```{r}
raw_values = data_complete_mod %>%
  select(subjectID, construct, pgACC, vmPFC, VS)

raw_values$predicted_logit = predict(model_2, newdata = raw_values, re.form = as.formula("~(1 | subjectID)"))

raw_values = raw_values %>%
  gather(roi, x, pgACC, VS, vmPFC) %>%
  rename("group" = construct) %>%
  mutate(predicted = logit2prob(predicted_logit))

vals = seq(round(min(raw_values$x),1), round(max(raw_values$x), 1), .2)

predicted = ggeffect(model_2, terms = c("pgACC [vals]", "construct")) %>%
  data.frame() %>%
  mutate(roi = "pgACC") %>%
  bind_rows(ggeffect(model_2, terms = c("VS [vals]", "construct")) %>%
    data.frame() %>%
    mutate(roi = "VS")) %>%
  bind_rows(ggeffect(model_2, terms = c("vmPFC [vals]", "construct")) %>%
    data.frame() %>%
    mutate(roi = "vmPFC"))

predicted %>%
  ggplot(aes(x, predicted, fill = group)) +
  geom_point(data = raw_values, aes(color = group), alpha = .1, size = .5) + 
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2) +
  geom_line(aes(color = group), size = 1.5) +
  facet_grid(~roi) +
  scale_color_manual(values = constructs, name = "") + 
  scale_fill_manual(values = constructs, name = "") + 
  scale_x_continuous(breaks = seq(-6, 6, 2)) +
  labs(x = "\nparameter estimate (SD)", y = "probability of responding yes\n") + 
  plot_aes
```

### by ROI
```{r}
predicted %>%
  ggplot(aes(x, predicted, fill = roi)) +
  geom_point(data = raw_values, aes(color = roi), alpha = .1, size = .5) + 
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2) +
  geom_line(aes(color = roi), size = 1.5) +
  facet_grid(~group) +
  scale_color_manual(values = rois, name = "") + 
  scale_fill_manual(values = rois, name = "") + 
  scale_x_continuous(breaks = seq(-6, 6, 2)) +
  labs(x = "\nparameter estimate (SD)", y = "probability of responding yes\n") + 
  plot_aes
```

