---
title: "Trial-level analyses: change"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)
```

This code reproduces the trial-level analyses including the change condition reported in the following manuscript:

[Cosme, D., Mobasser, A., & J. H. Pfeifer. If you’re happy and you know it: Neural correlates of self-evaluated psychological health and well-being](https://psyarxiv.com/86n3b/)

# load packages
```{r, message=FALSE, warning=FALSE}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse, gtools, GGally, sjstats, lme4, lmerTest, knitr, ggeffects, kableExtra, wesanderson, modelbased, install = TRUE)
```

# define aesthetics
```{r}
rois = c("#006989", "#56445D", "#8EC922")
constructs = c("#FEC601", "#254E70", "#F43C13")
instructions = wesanderson::wes_palette("Darjeeling1", 2, "continuous")
valence = c("#119DA4", "#19647E")
plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

# define functions
```{r}
model_table = function(model) {
  model %>%
    broom.mixed::tidy(., conf.int = TRUE) %>%
    filter(effect == "fixed") %>%
    rename("SE" = std.error,
           "z" = statistic,
           "p" = p.value) %>%
    mutate(term = gsub("\\(Intercept\\)", "Intercept", term),
           term = gsub("log\\(RT\\)", "RT", term),
           term = gsub("constructill-being", "Construct (ill-being)", term),
           term = gsub("constructsocial well-being", "Construct (social well-being)", term),
           term = gsub("instructionchange", "Instructions (change)", term),
           term = gsub(":", " x ", term),
           p = ifelse(p < .001, "< .001",
                      ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
           `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high),
           z = abs(round(z, 2))) %>%
    select(term, `b [95% CI]`, z, p) %>%
    kable() %>%
    kableExtra::kable_styling()

}
```

# load data
```{r}
task = read.csv("../../data/task_data.csv") %>%
  mutate(responseYN = as.factor(responseYN),
         construct = recode(construct, "well-being" = "self-oriented well-being",
                            "social" = "social well-being"),
         construct = factor(construct, levels = c("self-oriented well-being", "social well-being", "ill-being")),
         valence = factor(valence, levels = c("positive", "negative")))
betas = read.csv("../../data/neuro_data_2s.csv")
```

# exclude outliers and standardize
* Exclude outlier trials that are > 3 SDs from roi median across participants

```{r}
trial_conditions = task %>%
  select(subjectID, trial, run, instruction)

betas_outlier = betas %>%
  left_join(., trial_conditions) %>%
  filter(!is.na(meanPE)) %>%
  filter(!(run == "run2" & subjectID %in% c("FP067", "FP114"))) %>%
  group_by(roi) %>%
  mutate(median = median(meanPE, na.rm = TRUE),
         sd3 = 3*sd(meanPE, na.rm = TRUE),
         outlier = ifelse(meanPE > median + sd3 | meanPE < median - sd3, "yes", "no")) 

betas_outlier %>%
  group_by(outlier) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(total = sum(n),
         percent = round((n / total) * 100, 2)) %>%
  kable(format = "pandoc")

betas_ex = betas_outlier %>%
  filter(outlier == "no") %>%
  select(-c(median, sd3, outlier))
```

# merge data and exclude participants
* Motion exclusions: FP091
* Technical failure: FP080, FP082
* Non-compliance: FP021, FP049, FP085, FP121
* Standardize within participant and ROI

```{r}
data_ex = task %>%
  left_join(., betas_ex) %>%
  filter(!subjectID %in% c("FP091", "FP080", "FP082", "FP021", "FP049", "FP085", "FP121")) %>%
  filter(!is.na(meanPE)) %>%
  group_by(roi, subjectID) %>%
  mutate(std = meanPE / sd(meanPE, na.rm = TRUE)) %>%
  select(-sdPE)
```

# remove missing data for MLM analysis
```{r}
data_complete_mod = data_ex %>%
  select(-meanPE) %>%
  spread(roi, std) %>%
  select(subjectID, trial, run, instruction, construct, item, valence, response, responseYN, RT, pgACC, vmPFC, VS) %>%
  na.omit() %>%
  mutate(instruction = factor(instruction, levels = c("self", "change")))
```

# item responses {.tabset}
## percent endorsements
```{r}
percents = data_complete_mod %>%
  group_by(instruction, construct, item, response) %>%
  summarize(n = n()) %>%
  spread(response, n) %>%
  mutate(no = ifelse(is.na(no), 0, no),
         yes = ifelse(is.na(yes), 0, yes),
         total = no + yes) %>%
  gather(response, n, no, yes) %>%
  mutate(percent = round((n/total) * 100, 1),
         n = sprintf("%s / %s", n, total)) %>%
  filter(response == "yes")

percents %>%
  select(-response, -total, -n) %>%
  spread(instruction, percent) %>%
  arrange(desc(change)) %>%
  kable() %>%
  kableExtra::kable_styling()
```

## percent endorsements for improperly randomized items
```{r}
percents %>%
  filter(total < 10) %>%
  select(-response, -total, -n) %>%
  spread(instruction, percent) %>%
  arrange(desc(construct)) %>%
  kable() %>%
  kableExtra::kable_styling()
```

## plot
```{r}
data_complete_mod %>%
  group_by(instruction, construct, item, responseYN) %>%
  summarize(n = n()) %>%
  spread(responseYN, n) %>%
  mutate(no = ifelse(is.na(no), 0, no),
         yes = ifelse(is.na(yes), 0, yes),
         total = no + yes) %>%
  gather(responseYN, n, no, yes) %>%
  mutate(percent = round((n/total) * 100, 1)) %>%
  filter(responseYN == "yes") %>%
  ggplot(aes(percent, fill = instruction)) +
  geom_density(color = NA, alpha = .8) +
  facet_grid(~construct) +
  scale_fill_manual(values = instructions) +
  labs(x = "\n percent endorsed") +
  plot_aes
```

# ROI descriptives {.tabset}
## self trials
```{r}
# correlations
pgACC_vmPFC = data_complete_mod %>%
  filter(instruction == "self") %>%
   mutate(subjectID = as.factor(subjectID)) %>%
   select(subjectID, pgACC, vmPFC) %>%
   rmcorr::rmcorr(subjectID, pgACC, vmPFC, .)

pgACC_VS = data_complete_mod %>%
  filter(instruction == "self") %>%
   mutate(subjectID = as.factor(subjectID)) %>%
   select(subjectID, pgACC, VS) %>%
   rmcorr::rmcorr(subjectID, pgACC, VS, .)

vmPFC_VS = data_complete_mod %>%
  filter(instruction == "self") %>%
   mutate(subjectID = as.factor(subjectID)) %>%
   select(subjectID, vmPFC, VS) %>%
   rmcorr::rmcorr(subjectID, vmPFC, VS, .)

# means and SDs
mean_table = data_complete_mod %>%
  gather(roi, value, pgACC, vmPFC, VS) %>%
  group_by(roi) %>%
  summarize(M = round(mean(value, na.rm = TRUE), 2),
            SD = round(sd(value, na.rm = TRUE), 2)) %>%
  mutate(order = ifelse(roi == "pgACC", 1,
                 ifelse(roi == "vmPFC", 2, 3)),
         roi = ifelse(roi == "pgACC", "1. pgACC",
               ifelse(roi == "vmPFC", "2. vmPFC", "3. VS"))) %>%
  rename("ROI" = roi) %>%
  arrange(order) %>%
  select(-order)

# table
corr_table = data.frame(ROI = c("1. pgACC", "2. vmPFC", "3. VS"),
           `1` = c("--", paste0(round(pgACC_vmPFC[[1]],2), " [",round(pgACC_vmPFC[[4]][1],2),", ",round(pgACC_vmPFC[[4]][2],2),"]"),
                   paste0(round(pgACC_VS[[1]],2), " [",round(pgACC_VS[[4]][1],2),", ",round(pgACC_VS[[4]][2],2),"]")),
           `2` = c("", "--", paste0(round(vmPFC_VS[[1]],2), " [",round(vmPFC_VS[[4]][1],2),", ",round(vmPFC_VS[[4]][2],2),"]")),
           `3` = c("", "", "--"),
           check.names = FALSE)

mean_table %>%
  full_join(., corr_table) %>%
  knitr::kable(format = "pandoc", caption = "Repeated Measures Correlations Between ROIs (n = 3694). All correlations are statistically significant, p < .001. 95% confidence intervals are bracketed")
```

## change trials
```{r}
# correlations
pgACC_vmPFC = data_complete_mod %>%
  filter(instruction == "change") %>%
   mutate(subjectID = as.factor(subjectID)) %>%
   select(subjectID, pgACC, vmPFC) %>%
   rmcorr::rmcorr(subjectID, pgACC, vmPFC, .)

pgACC_VS = data_complete_mod %>%
  filter(instruction == "change") %>%
   mutate(subjectID = as.factor(subjectID)) %>%
   select(subjectID, pgACC, VS) %>%
   rmcorr::rmcorr(subjectID, pgACC, VS, .)

vmPFC_VS = data_complete_mod %>%
  filter(instruction == "change") %>%
   mutate(subjectID = as.factor(subjectID)) %>%
   select(subjectID, vmPFC, VS) %>%
   rmcorr::rmcorr(subjectID, vmPFC, VS, .)

# means and SDs
mean_table = data_complete_mod %>%
  gather(roi, value, pgACC, vmPFC, VS) %>%
  group_by(roi) %>%
  summarize(M = round(mean(value, na.rm = TRUE), 2),
            SD = round(sd(value, na.rm = TRUE), 2)) %>%
  mutate(order = ifelse(roi == "pgACC", 1,
                 ifelse(roi == "vmPFC", 2, 3)),
         roi = ifelse(roi == "pgACC", "1. pgACC",
               ifelse(roi == "vmPFC", "2. vmPFC", "3. VS"))) %>%
  rename("ROI" = roi) %>%
  arrange(order) %>%
  select(-order)

# table
corr_table = data.frame(ROI = c("1. pgACC", "2. vmPFC", "3. VS"),
           `1` = c("--", paste0(round(pgACC_vmPFC[[1]],2), " [",round(pgACC_vmPFC[[4]][1],2),", ",round(pgACC_vmPFC[[4]][2],2),"]"),
                   paste0(round(pgACC_VS[[1]],2), " [",round(pgACC_VS[[4]][1],2),", ",round(pgACC_VS[[4]][2],2),"]")),
           `2` = c("", "--", paste0(round(vmPFC_VS[[1]],2), " [",round(vmPFC_VS[[4]][1],2),", ",round(vmPFC_VS[[4]][2],2),"]")),
           `3` = c("", "", "--"),
           check.names = FALSE)

mean_table %>%
  full_join(., corr_table) %>%
  knitr::kable(format = "pandoc", caption = "Repeated Measures Correlations Between ROIs (n = 3687). All correlations are statistically significant, p < .001. 95% confidence intervals are bracketed")
```

# model each construct separately {.tabset}
## self-oriented well-being {.tabset}
```{r}
model_rt_wellbeing = glmer(responseYN ~ RT * instruction + 
                     pgACC * instruction + vmPFC * instruction + VS * instruction +
                     (1 | subjectID), 
                family = binomial, 
                data = filter(data_complete_mod, construct == "self-oriented well-being"),
                control = glmerControl(optimizer = "bobyqa"))
```

### model summary
```{r}
summary(model_rt_wellbeing)
```

### model table
```{r}
model_table(model_rt_wellbeing)
```

## social well-being {.tabset}
```{r}
model_rt_social = glmer(responseYN ~ RT * instruction + 
                     pgACC * instruction + vmPFC * instruction + VS * instruction +
                     (1 | subjectID), 
                family = binomial, 
                data = filter(data_complete_mod, construct == "social well-being"),
                control = glmerControl(optimizer = "bobyqa"))
```

### model summary
```{r}
summary(model_rt_social)
```

### model table
```{r}
model_table(model_rt_social)
```

## ill-being {.tabset}
```{r}
model_rt_illbeing = glmer(responseYN ~ RT * instruction + 
                     pgACC * instruction + vmPFC * instruction + VS * instruction +
                     (1 | subjectID), 
                family = binomial, 
                data = filter(data_complete_mod, construct == "ill-being"),
                control = glmerControl(optimizer = "bobyqa"))
```

### model summary
```{r}
summary(model_rt_illbeing)
```

### model table
```{r}
model_table(model_rt_illbeing)
```

## plot predicted effects {.tabset}
### by construct
```{r, fig.height=8}
raw_values = data_complete_mod %>%
  select(subjectID, construct, instruction, RT, pgACC, vmPFC, VS) %>%
 gather(roi, x, pgACC, VS, vmPFC)

vals = seq(round(min(raw_values$x),1), round(max(raw_values$x), 1), .5)

predicted_sub = ggpredict(model_rt_wellbeing, terms = c("pgACC [vals]", "instruction", "subjectID"), type = "random") %>%
  data.frame() %>%
  mutate(roi = "pgACC",
         construct = "self-oriented well-being") %>%
  bind_rows(ggpredict(model_rt_wellbeing, terms = c("VS [vals]", "instruction", "subjectID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "VS",
                     construct = "self-oriented well-being")) %>%
  bind_rows(ggpredict(model_rt_wellbeing, terms = c("vmPFC [vals]", "instruction", "subjectID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "vmPFC",
                     construct = "self-oriented well-being")) %>%
  bind_rows(ggpredict(model_rt_social, terms = c("pgACC [vals]", "instruction", "subjectID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "pgACC",
                     construct = "social well-being")) %>%
  bind_rows(ggpredict(model_rt_social, terms = c("VS [vals]", "instruction", "subjectID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "VS",
                     construct = "social well-being")) %>%
  bind_rows(ggpredict(model_rt_social, terms = c("vmPFC [vals]", "instruction", "subjectID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "vmPFC",
                     construct = "social well-being")) %>%
  bind_rows(ggpredict(model_rt_illbeing, terms = c("pgACC [vals]", "instruction", "subjectID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "pgACC",
                     construct = "ill-being")) %>%
  bind_rows(ggpredict(model_rt_illbeing, terms = c("VS [vals]", "instruction", "subjectID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "VS",
                     construct = "ill-being")) %>%
  bind_rows(ggpredict(model_rt_illbeing, terms = c("vmPFC [vals]", "instruction", "subjectID"), type = "random") %>%
              data.frame() %>%
              mutate(roi = "vmPFC",
                     construct = "ill-being")) %>%
  mutate(construct = factor(construct, levels = c("self-oriented well-being", "social well-being", "ill-being")))

predicted = ggeffect(model_rt_wellbeing, terms = c("pgACC [vals]", "instruction")) %>%
  data.frame() %>%
  mutate(roi = "pgACC",
         construct = "self-oriented well-being") %>%
  bind_rows(ggeffect(model_rt_wellbeing, terms = c("VS [vals]", "instruction")) %>%
              data.frame() %>%
              mutate(roi = "VS",
                     construct = "self-oriented well-being")) %>%
  bind_rows(ggeffect(model_rt_wellbeing, terms = c("vmPFC [vals]", "instruction")) %>%
              data.frame() %>%
              mutate(roi = "vmPFC",
                     construct = "self-oriented well-being")) %>%
  bind_rows(ggeffect(model_rt_social, terms = c("pgACC [vals]", "instruction")) %>%
              data.frame() %>%
              mutate(roi = "pgACC",
                     construct = "social well-being")) %>%
  bind_rows(ggeffect(model_rt_social, terms = c("VS [vals]", "instruction")) %>%
              data.frame() %>%
              mutate(roi = "VS",
                     construct = "social well-being")) %>%
  bind_rows(ggeffect(model_rt_social, terms = c("vmPFC [vals]", "instruction")) %>%
              data.frame() %>%
              mutate(roi = "vmPFC",
                     construct = "social well-being")) %>%
  bind_rows(ggeffect(model_rt_illbeing, terms = c("pgACC [vals]", "instruction")) %>%
              data.frame() %>%
              mutate(roi = "pgACC",
                     construct = "ill-being")) %>%
  bind_rows(ggeffect(model_rt_illbeing, terms = c("VS [vals]", "instruction")) %>%
              data.frame() %>%
              mutate(roi = "VS",
                     construct = "ill-being")) %>%
  bind_rows(ggeffect(model_rt_illbeing, terms = c("vmPFC [vals]", "instruction")) %>%
              data.frame() %>%
              mutate(roi = "vmPFC",
                     construct = "ill-being")) %>%
  mutate(construct = factor(construct, levels = c("self-oriented well-being", "social well-being", "ill-being")))

predicted %>%
  ggplot(aes(x, predicted)) +
  geom_line(data = predicted_sub, aes(color = construct, group = interaction(construct, group, facet)), size = .25, alpha = .5) +
  geom_line(aes(color = construct), size = 2) +
  facet_grid(group~roi) +
  scale_color_manual(values = constructs, name = "") + 
  scale_fill_manual(values = constructs, name = "") + 
  scale_x_continuous(breaks = seq(-6, 6, 2)) +
  labs(x = "\nparameter estimate (SD)", y = "probability of responding yes\n") + 
  plot_aes
```

### by instruction
```{r, fig.height=9}
predicted %>%
  ggplot(aes(x, predicted)) +
  geom_line(data = predicted_sub, aes(color = group, group = interaction(group, roi, facet)), size = .25, alpha = .5) +
  geom_line(aes(color = group), size = 2) +
  facet_grid(construct~roi) +
  scale_color_manual(values = instructions, name = "") + 
  scale_fill_manual(values = instructions, name = "") + 
  scale_x_continuous(breaks = seq(-6, 6, 2)) +
  labs(x = "\nparameter estimate (SD)", y = "probability of responding yes\n") + 
  plot_aes
```

### by ROI
```{r, fig.height=8}
predicted %>%
  ggplot(aes(x, predicted)) +
  geom_line(data = predicted_sub, aes(color = roi, group = interaction(group, roi, facet)), size = .25, alpha = .5) +
  geom_line(aes(color = roi), size = 2) +
  facet_grid(group~construct) +
  scale_color_manual(values = rois, name = "") + 
  scale_fill_manual(values = rois, name = "") + 
  scale_x_continuous(breaks = seq(-6, 6, 2)) +
  labs(x = "\nparameter estimate (SD)", y = "probability of responding yes\n") + 
  plot_aes
```
