---
title: "Individual difference analysis"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
```

This code reproduces the individual difference analyses reported in the following manuscript:

[Cosme, D., Mobasser, A., & J. H. Pfeifer. If you’re happy and you know it: Neural correlates of self-evaluated psychological health and well-being](https://psyarxiv.com/86n3b/)

# load packages
```{r, message=FALSE, warning=FALSE}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse, gtools, GGally, sjstats, lme4, lmerTest, knitr, ggeffects, kableExtra, install = TRUE)
```

# define aesthetics
```{r}
rois = c("#006989", "#56445D", "#8EC922")
constructs = c("#FEC601", "#254E70", "#F43C13")
instructions = wesanderson::wes_palette("Darjeeling1", 2, "continuous")
valence = c("#119DA4", "#19647E")
plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 12),
        text = element_text(size = 16, family = "Futura Medium"),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank())
```

# define functions
```{r}
model_table = function(model) {
  model %>%
    broom::tidy(., conf.int = TRUE) %>%
    rename("SE" = std.error,
           "t" = statistic,
           "p" = p.value) %>%
    mutate(term = gsub("\\(Intercept\\)", "Intercept", term),
           p = ifelse(p < .001, "< .001",
                      ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
           `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high),
           t = abs(round(t, 2)))  %>%
    select(term, `b [95% CI]`, t, p)
}

model_table_percent = function(model) {
  model %>%
    broom.mixed::tidy(., conf.int = TRUE) %>%
    filter(effect == "fixed") %>%
    rename("SE" = std.error,
           "t" = statistic,
           "p" = p.value) %>%
    mutate(term = gsub("\\(Intercept\\)", "Intercept", term),
           term = gsub("constructill-being", "Construct (ill-being)", term),
           term = gsub("constructsocial", "Construct (social well-being)", term),
           term = gsub("instructionself", "Instructions (self)", term),
           term = gsub(":", " x ", term),
           p = ifelse(p < .001, "< .001",
                      ifelse(p == 1, "1.000", gsub("0.(.*)", ".\\1", sprintf("%.3f", p)))),
           `b [95% CI]` = sprintf("%.2f [%0.2f, %.2f]", estimate, conf.low, conf.high),
           t = abs(round(t, 2))) %>%
    select(term, `b [95% CI]`, df, t, p) %>%
    kable(digits = 2) %>%
    kableExtra::kable_styling()

}
```

# load data
```{r}
task = read.csv("../../data/task_percent_data.csv")
rois = read.csv("../../data/neuro_average_data.csv")
```

# exclude outliers and standardize
* exclude outlier values that are > 3 SDs from roi median across subs
* standardize within roi
```{r}
rois_ex = rois %>%
  group_by(roi, contrast) %>%
  mutate(median = median(meanPE, na.rm = TRUE),
         sd3 = 3*sd(meanPE, na.rm = TRUE),
         outlier = ifelse(meanPE > median + sd3 | meanPE < median - sd3, "yes", "no")) %>%
  filter(outlier == "no") %>%
  select(-c(median, sd3, sdPE, outlier)) %>%
  group_by(roi) %>%
  mutate(sd.roi = sd(meanPE, na.rm = TRUE),
         std = meanPE / sd.roi) %>%
  select(-meanPE, -sd.roi) %>%
  spread(roi, std)
```

# exclude subs
* Motion exclusions: FP091
* Technical failure: FP080, FP082
* Non-compliance: FP021, FP049, FP085, FP121
* Missing run 2: FP067, FP114

```{r}
data_ex = task %>%
  mutate(construct = factor(construct, levels = c("well-being", "ill-being", "social"))) %>%
  filter(!subjectID %in% c("FP091", "FP080", "FP082", "FP021", "FP049", "FP085", "FP121", "FP067", "FP114"))

data_complete = data_ex %>%
  left_join(., rois_ex) %>%
  filter(instruction == "self") %>%
  select(construct, subjectID, percent, contrast, pgACC, vmPFC, VS) %>%
  unique() %>%
  gather(roi, value, pgACC, vmPFC, VS) %>%
  unite(con_roi, contrast, roi) %>%
  filter(!is.na(value)) %>%
  spread(con_roi, value) %>%
  ungroup() %>%
  rename("pgACC" = self_pgACC,
         "vmPFC" = self_vmPFC,
         "VS" = self_VS) %>%
  na.omit()

data_percent = data_ex %>%
  select(construct, instruction, subjectID, percent) %>%
  unique()
```

# behavioral analyses {.tabset}
## descriptives
```{r}
data_percent %>%
  group_by(construct, instruction) %>%
  summarize(n = n(),
            mean = mean(percent, na.rm = TRUE),
            sd = sd(percent, na.rm = TRUE)) %>%
  arrange(instruction) %>%
  mutate_if(is.numeric, round, 2) %>%
  select(instruction, everything()) %>%
  kable() %>%
  kable_styling()
```

## run model
```{r}
model_percent = lmer(percent ~ construct*instruction + (1 | subjectID), data = data_percent)
```

## model summary
```{r}
summary(model_percent)
```

## model table
```{r}
model_table_percent(model_percent)
```

## model fit
```{r}
performance::r2(model_percent)
```

## plot predicted effects
```{r}
raw_values = data_percent %>%
  rename("predicted" = percent,
         "x" = construct,
         "group" = instruction) %>%
  mutate(x = recode(x, "well-being" = "self-oriented well-being",
                            "social" = "social well-being"),
         x = factor(x, levels = c("self-oriented well-being", "social well-being", "ill-being")))

predicted = ggeffect(model_percent, terms = c("construct", "instruction")) %>%
  data.frame() %>%
  mutate(x = recode(x, "well-being" = "self-oriented well-being",
                            "social" = "social well-being"),
         x = factor(x, levels = c("self-oriented well-being", "social well-being", "ill-being")))

predicted %>%
  ggplot(aes(x, predicted, color = group)) +
  geom_line(data = raw_values, aes(color = group, group = interaction(group, subjectID)), size = .25, alpha = .3) +
  geom_line(aes(group = group), size = 1.5) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high), size = 1, linewidth = 1) +
  scale_color_manual(values = instructions, name = "") +
  labs(x = "", y = "percent yes\n") +
  plot_aes
```

# neural analyses {.tabset}
## multilevel models
```{r}
model_0 = lmer(percent ~ construct + (1 | subjectID), data = data_complete,
               control = lmerControl(optimizer = "bobyqa"))
model_1 = lmer(percent ~ construct*pgACC  + (1 | subjectID), data = data_complete,
               control = lmerControl(optimizer = "bobyqa"))
model_2 = lmer(percent ~ construct*pgACC + construct*vmPFC + (1 | subjectID), data = data_complete,
               control = lmerControl(optimizer = "bobyqa"))
model_3 = lmer(percent ~ construct*pgACC + construct*vmPFC + construct*VS + (1 | subjectID), data = data_complete,
               control = lmerControl(optimizer = "bobyqa"))

anova(model_0, model_1, model_2, model_3)
```

## separate models {.tabset}
Since the models did not converge, we fit linear regression models for each construct separately

### well-being
```{r}
model_wellbeing =  lm(percent ~ pgACC + vmPFC + VS, data = filter(data_complete, construct == "well-being"))
summary(model_wellbeing)
```

### ill-being
```{r}
model_illbeing = lm(percent ~ pgACC + vmPFC + VS, data = filter(data_complete, construct == "ill-being"))
summary(model_illbeing)
```

### social
```{r}
model_social = lm(percent ~ pgACC + vmPFC + VS, data = filter(data_complete, construct == "social"))
summary(model_social)
```

### model table
```{r}
 model_table(model = model_wellbeing) %>% mutate(model = "self-oriented well-being") %>%
  bind_rows(model_table(model = model_social) %>% mutate(model = "social well-being")) %>%
  bind_rows(model_table(model = model_illbeing) %>% mutate(model = "ill-being")) %>%
  select(model, everything()) %>%
  kable() %>%
  kableExtra::kable_styling()
```

### plot predicted effects
```{r}
raw_values = data_complete %>%
  select(-contains("change")) %>%
  select(subjectID, construct, percent, pgACC, vmPFC, VS) %>%
  gather(roi, x,  pgACC, vmPFC, VS) %>%
  rename("predicted" = percent) %>%
  mutate(construct = recode(construct, "well-being" = "self-oriented well-being",
                            "social" = "social well-being"),
         construct = factor(construct, levels = c("self-oriented well-being", "social well-being", "ill-being")))

vals = seq(round(min(raw_values$x),1), round(max(raw_values$x), 1), .5)

predicted = ggeffect(model_wellbeing, terms = c("pgACC [vals]")) %>%
  data_frame() %>%
  mutate(roi = "pgACC",
         construct = "self-oriented well-being") %>%
  bind_rows(ggeffect(model_wellbeing, terms = c("VS [vals]")) %>%
              data_frame() %>%
              mutate(roi = "VS",
                     construct = "self-oriented well-being")) %>%
  bind_rows(ggeffect(model_wellbeing, terms = c("vmPFC [vals]")) %>%
              data_frame() %>%
              mutate(roi = "vmPFC",
                     construct = "self-oriented well-being")) %>%
  bind_rows(ggeffect(model_social, terms = c("pgACC [vals]")) %>%
              data_frame() %>%
              mutate(roi = "pgACC",
                     construct = "social well-being")) %>%
  bind_rows(ggeffect(model_social, terms = c("VS [vals]")) %>%
              data_frame() %>%
              mutate(roi = "VS",
                     construct = "social well-being")) %>%
  bind_rows(ggeffect(model_social, terms = c("vmPFC [vals]")) %>%
              data_frame() %>%
              mutate(roi = "vmPFC",
                     construct = "social well-being")) %>%
  bind_rows(ggeffect(model_illbeing, terms = c("pgACC [vals]")) %>%
              data_frame() %>%
              mutate(roi = "pgACC",
                     construct = "ill-being")) %>%
  bind_rows(ggeffect(model_illbeing, terms = c("VS [vals]")) %>%
              data_frame() %>%
              mutate(roi = "VS",
                     construct = "ill-being")) %>%
  bind_rows(ggeffect(model_illbeing, terms = c("vmPFC [vals]")) %>%
              data_frame() %>%
              mutate(roi = "vmPFC",
                     construct = "ill-being")) %>%
  mutate(construct = factor(construct, levels = c("self-oriented well-being", "social well-being", "ill-being")))

predicted %>%
  ggplot(aes(x, predicted)) +
  geom_point(data = raw_values, aes(x, predicted, color = construct), alpha = .25) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = construct), alpha = .5) +
  geom_line(aes(color = construct), size = 2) +
  facet_grid(~roi) +
  scale_color_manual(values = constructs, name = "") + 
  scale_fill_manual(values = constructs, name = "") + 
  scale_x_continuous(breaks = seq(-6, 6, 2)) +
  labs(x = "\nmean parameter estimate (SD)", y = "percent yes\n") + 
  plot_aes
```

