---
title: "SVC factor analysis"
author: "Dani Cosme & Arian Mobasser"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    highlight: tango
    theme: united
    toc: true
    toc_float: 
      collapsed: TRUE
      smooth_scroll: TRUE
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# load packages
```{r}
if (!require(tidyverse)) {
  install.packages('tidyverse')
}

if (!require(psych)) {
  install.packages('psych')
}

if (!require(rio)) {
  install.packages('rio')
}
```

# define variables and paths
* `cred_file_location` = path to your Qualtrics credential file. You'll need to generate this via Qualtrics using the instructions above.
* `id_column_name` = subject ID column name in Qualtrics survey; can be a regular expression
```{r, echo = FALSE}
cred_file_location = '~/credentials.yaml.DEFAULT'
sid_column_name = '(Finished|id)'
survey_name_filter = 'Netzel'
identifiableData = c('Name', 'EmailAddress', 'IPAddress', 'Check', 'AMAZON_UO_TEXT', 'AMAZON_TEXT', 'CELL', 'CELL_TEXT', 'EMAIL', 'EMAIL_UO', 'PARENT', 'EMAIL_TEXT', 'EMAIL_UO_TEXT', 'PARENT_CELL', 'cell', 'email_personal', 'email_UO') # exclude when printing duplicates
output_file_dir = '~/Documents/code/dsnlab/FP_scripts/behavioral/SONA/netzel/'
```

# access qualtrics data
Filter available surveys based on the filter specified above.
```{r, results = "hide"}
# load credential file
credentials = scorequaltrics::creds_from_file(cred_file_location)

# filter
surveysAvail = scorequaltrics::get_surveys(credentials)
surveysFiltered = filter(surveysAvail, grepl(survey_name_filter, SurveyName))

knitr::kable(arrange(select(surveysFiltered, SurveyName), SurveyName))
```

# load data
```{r getsurveydata, results = "hide", }
# get survey data
svc_data = scorequaltrics::get_survey_data(surveysFiltered, credentials, pid_col = sid_column_name) %>%
  filter(!item %in% identifiableData) %>% #filter out identifiable data
  filter(grepl("SVC|SEX|Date", item)) %>%
  mutate(value = ifelse(value == "5", NA, #code prefer not to respond as NA
                 ifelse(value == "", NA, value))) %>%
  spread(item, value) %>%
  mutate(SEX = ifelse(SEX == 1, "female", "male")) %>%
  mutate(StartDate = as.POSIXct(StartDate),
         EndDate = as.POSIXct(EndDate),
         duration = round(difftime(EndDate, StartDate, units = 'mins'), 1)) %>%
  select(id, SEX, duration, starts_with("SVC")) %>%
  mutate_at(vars(starts_with("SVC")), funs(as.numeric))
 
# load svc item names
svc_items = import("~/Documents/code/dsnlab/FP_scripts/behavioral/SONA/netzel/SVC_itemnames.xlsx") %>%
    t() %>%
    as.data.frame() %>%
    rename("text" = `1`) %>%
    extract(text, "text", ".*- (.*)") %>%
    mutate(item = rownames(.))
```

# exclude subjects
* those who didn't complete the survey
* those with responded the same for all questions
* those who completed the survey too quickly
```{r examine svc}
svc = svc_data %>%
  filter(!(is.na(SVC_1) & is.na(SVC_2) & is.na(SVC_3))) %>%
  filter(duration >= 6.5)
```

# print data
```{r}
svc %>%
  arrange(duration)
```

# demographics
```{r}
svc %>%
  group_by(SEX) %>%
  summarize(n = n())
```

# scree plot
```{r}
VSS.scree(cor(svc[,-c(1:3)], use = "pairwise.complete.obs"))
```

# PCA, 6 factors, no rotation
## Run PCA
```{r}
pca.var = principal(svc[,-c(1:3)], rotate = "none", nfactors = 6, missing = TRUE)
loadings = data.frame(loading = pca.var$loadings[,1:6]) %>%
  mutate(item = rownames(.))

pca.var
```

## Merge items and loadings
```{r}
merged = loadings %>%
    left_join(., svc_items, by = "item") %>% 
    select(item, text, everything())
```

## Sort by loading on component 1
```{r}
merged %>%
  arrange(desc(loading.PC1))
```

## Sort by loading on component 2
```{r}
merged %>%
  arrange(desc(loading.PC2)) %>%
  select(item, text, loading.PC2, everything())
```

## Sort by loading on component 3
```{r}
merged %>%
  arrange(desc(loading.PC3)) %>%
  select(item, text, loading.PC3, everything())
```

## Sort by loading on component 4
```{r}
merged %>%
  arrange(desc(loading.PC4)) %>%
  select(item, text, loading.PC4, everything())
```

## Sort by loading on component 5
```{r}
merged %>%
  arrange(desc(loading.PC5)) %>%
  select(item, text, loading.PC5, everything())
```

## Sort by loading on component 6
```{r}
merged %>%
  arrange(desc(loading.PC6)) %>%
  select(item, text, loading.PC6, everything())
```

# PCA, 3 factors promax
## Run PCA
```{r}
pca.var2 = principal(svc[,-c(1:3)], rotate = "promax", nfactors = 3, missing = TRUE)
loadings2 = data.frame(loading = pca.var2$loadings[,1:3]) %>%
  mutate(item = rownames(.))

pca.var2
```

## Merge items and loadings
```{r}
merged = loadings2 %>%
    left_join(., svc_items, by = "item") %>% 
    select(item, text, everything())
```

## Sort by loading on component 1
```{r}
merged %>%
  arrange(desc(loading.RC1)) %>%
  slice(1:30)
```

## Sort by loading on component 2
```{r}
merged %>%
  arrange(desc(loading.RC2)) %>%
  slice(1:40)
```

## Sort by loading on component 3
```{r}
merged %>%
  arrange(desc(loading.RC3))
```

## Sort by loading on component 4
```{r}
merged %>%
  arrange(desc(loading.RC4))
```

# choose words
```{r}
words = left_join(merged, select(loadings, item, loading.PC1)) %>%
  rename("social" = loading.RC1,
         "ill-being" = loading.RC2,
         "health" = loading.RC3,
         "well-being" = loading.PC1)

wellbeing = words %>%
  arrange(desc(`well-being`)) %>%
  slice(1:40) %>%
  filter(!item %in% c("SVC_135","SVC_122","SVC_134","SVC_98","SVC_142","SVC_131","SVC_138","SVC_142","SVC_27","SVC_115","SVC_114","SVC_139","SVC_162","SVC_130","SVC_60","SVC_168","SVC_141","SVC_120","SVC_30","SVC_91","SVC_121", "SVC_83", "SVC_40")) %>%
  bind_cols(condition = rep(1,length(.$text)),
            reverse = rep(0,length(.$text)),
            syllables = c(2, 5, 6, 2, 3, 4, 6, 2, 2, 5, 4, 3, 3, 3, 2, 1, 5, 4)) %>%
  select(text, condition, reverse, syllables, item, everything())

social = words %>%
  arrange(desc(social)) %>%
  slice(1:28) %>%
  filter(!item %in% c("SVC_12", "SVC_156", "SVC_43", "SVC_102", "SVC_128", "SVC_120", "SVC_45", "SVC_99", "SVC_10","SVC_22","SVC_108","SVC_104","SVC_115", "SVC_100")) %>%
  bind_rows(filter(words, item %in% c("SVC_111","SVC_124","SVC_157","SVC_143"))) %>%
  bind_cols(condition = rep(2,length(.$text)),
            reverse = c(rep(0,14), rep(1,4)),
            syllables = c(3, 5, 3, 1, 2, 5, 6, 7, 4,3, 3, 2, 6, 4, 5, 4, 3, 2)) %>%
  select(text, condition, reverse, syllables, item, everything())

illbeing = words %>%
  arrange(desc(`ill-being`)) %>%
  slice(1:21) %>%
  filter(!item %in% c("SVC_94", "SVC_58", "SVC_143")) %>%
  bind_cols(condition = rep(3,length(.$text)),
            reverse = rep(0,length(.$text)),
            syllables = c(2, 3, 2, 5, 4, 2, 1, 1, 6, 3, 2, 2, 2, 5, 3, 2, 5, 3)) %>%
  select(text, condition, reverse, syllables, item, everything()) %>%
  mutate(text = ifelse(text == "fearful of being hurt", "afraid of being hurt", text))
```

# print words
## well-being
```{r}
wellbeing
```

## social
```{r}
social
```

## ill-being
```{r}
illbeing
```

# save words
```{r}
# write.table(wellbeing[,1:4], "~/Documents/code/dsnlab/svc/task/design/materials/wellbeing.txt", sep = ',', quote = FALSE, col.names = FALSE, row.names = FALSE)
# 
# write.table(social[,1:4], "~/Documents/code/dsnlab/svc/task/design/materials/social.txt", sep = ',', quote = FALSE, col.names = FALSE, row.names = FALSE)
# 
# write.table(illbeing[,1:4], "~/Documents/code/dsnlab/svc/task/design/materials/illbeing.txt", sep = ',', quote = FALSE, col.names = FALSE, row.names = FALSE)
```

